Make any stupid plot you want

### 2020-09-11 draft/intro.tex
cites + line or two

 What even is encoding?

 \begin{figure}
    %% Bertin's decomposition of an image
 \end{figure}
 \begin{figure}
    \includegraphics{figures/intro/retinal_variables}
    \label{fig:retinal_variable}
    \caption{This organization of Bertin's retinal variables \cite{bertinSemiologyGraphicsDiagrams2011} that lays out the geometry(marks) and corresponding aesthetic variations (channels) with a recommendation based on data type (qualitative versus quantative) comes from Krygier and Wood's Making Maps \cite{krygierMakingMapsVisual2005}}
\end{figure}

@@

Add table of which sorts of invariance a channel will preserve

@@

\section{Library Review}
\subsection{Grammar of Graphics \& ggplot}
\begin{figure}
    \includegraphics{figures/intro/grammar_chart_composition.png}
    \caption{page 10 (introduction)}
\end{figure}
\begin{figure}
    \includegraphics{figures/intro/grammar_example.png}
    \caption{Wilkenson decomposed a graphic into ...} 
\end{figure}
\cite{wilkinsonGrammarGraphicsStatistics2005}
charts - words 
    - instances of much more general objects (geometric primatives)
    - histogram =/= bar chart
graphics - statements 
expliceltly OO
    1. specification
        data - operations/computations
        trans - variable transforms (rank)
        scale - scale transforms
        coord - coordinate system
        element - marks and channels
        guide - meta elements - (axes, legends, etc)
    2. assembly - kinda what happens in artist (spec->something that can go to renderer) 
    3. display - rendering

@@

>>>>

 What even is encoding?
Bertin table on 69 rewrite here clearly  
 \begin{figure}
    %% Bertin's decomposition of an image
 \end{figure}
 \begin{figure}
    \includegraphics{figures/intro/retinal_variables}
    \label{fig:retinal_variable}
    \caption{This organization of Bertin's retinal variables \cite{bertinSemiologyGraphicsDiagrams2011} that lays out the geometry(marks) and corresponding aesthetic variations (channels) with a recommendation based on data type (qualitative versus quantative) comes from Krygier and Wood's Making Maps \cite{krygierMakingMapsVisual2005}}
\end{figure}

@@

Add table of which sorts of invariance a channel will preserve....

@@

\section{Library Review}
\subsection{Grammar of Graphics \& ggplot}
Specifies the end chart (graphic)
we want to specify the transformations ....
\begin{figure}
    \includegraphics{figures/intro/grammar_chart_composition.png}
    \caption{page 10 (introduction)}
\end{figure}
\begin{figure}
    \includegraphics{figures/intro/grammar_example.png}
    \caption{Wilkenson decomposed a graphic into ...} 
\end{figure}
\cite{wilkinsonGrammarGraphicsStatistics2005}
charts - words 
    - instances of much more general objects (geometric primatives)
    - histogram =/= bar chart
graphics - statements 
expliceltly OO
    1. specification
        data - operations/computations
        trans - variable transforms (rank)
        scale - scale transforms
        coord - coordinate system
        element - marks and channels
        guide - meta elements - (axes, legends, etc)
    2. assembly - kinda what happens in artist (spec->something that can go to renderer) 
    3. display - rendering

@@

ggplot - strictly hierarchal components (layers), matplotlib - transforms that mostly happen indepently 
"designing and producing statistical graphics is not an art" - ties in w/ difference between drawing program and visualization library, preservation of properties of measurement type and observation type
